---
title: "UNO_jobs_analysis"
author: "stewarta"
date: "22 January 2018"
output: html_document
---

The data I am analysing today is from the UNO website. It is from the careers page where they have all their job offers. They separate their jobs into different categories, which I all downloaded into different excel spreadsheets and parsed using the xlsx package into dataframes.

```{r}
library(xlsx)
library(ggplot2)
library(plyr)
jobsdf <- read.xlsx("UNO_jobs.xlsx", sheetName = "Feuil1")
head(jobsdf)
```

Let's see how often the same job families are wanted:

```{r, echo=FALSE}
plot <- ggplot(jobsdf, aes(x = jobsdf$Job.Family)) + geom_bar() + theme(axis.text.x  = element_text(angle=90, vjust=0, hjust = 1))
plot
```

more specific let's pull up the top 10

```{r, echo=FALSE}
tbl_jobs <- count(jobsdf$Job.Family)
print("top 10 jobs that have positions available:")
most_wanted_jobs <- tbl_jobs[order(-tbl_jobs$freq),]
head(most_wanted_jobs, n=10)
```

The dataframe also indicates the job level wanted but I had to look up what it means:

http://www.unfpa.org/resources/united-nations-staff-categories

Professional  (P) and Director (D) staff

P1 - No work experience required

P2 - Minimum of 2 years of work experience

P3 - Minimum of 5 years of work experience

P4 - Minimum of 7 years of work experience

P5 - Minimum of 10 years of work experience

D1 - Minimum of 15 years of work experience

D2 - More than 15 years of work experience

General Service  (G) staff

G1 - No work experience required

G2 - Minimum of 2 years of work experience

G3 - Minimum of 3 years of work experience

G4 - Minimum of 4 years of work experience

G5 - Minimum of 5 years of work experience

G6 - Minimum of 6 years of work experience

G7 - Minimum of 7 years of work experience

National Professional  Officers (NO)

NOA - No work experience required
NOB - Minimum of 2 years of work experience

NOC - Minimum of 5 years of work experience

NOD - Minimum of 7 years of work experience

```{r, echo=FALSE}
plot <- ggplot(jobsdf, aes(x = jobsdf$Level)) + geom_bar() + theme(axis.text.x  = element_text(angle=90, vjust=0, hjust = 1))
plot

```

So the most wanted kind of job is P3 - Minimum of 5 years of work experience followed by P4 - Minimum of 7 years of work experience. The number of P2 is very limited as is any position as director. It looks like non of us are going to be recruted right after PhD!

Now let's look at internships:

```{r, echo=FALSE}
internshipsdf <- read.xlsx("UNO_jobs_internships.xlsx", sheetName = "Feuil1")
head(jobsdf)
```