---
title: "UNO_jobs_analysis"
author: "stewarta"
date: "22 January 2018"
output: html_document
---

The data I am analysing today is from the UNO website. It is from the careers page where they have all their job offers. They separate their jobs into different categories, which I all downloaded into different excel spreadsheets and parsed using the xlsx package into dataframes.

# Jobs dataframe

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(xlsx)
library(ggplot2)
library(plyr)
library(knitr)
jobsdf <- read.xlsx("UNO_jobs.xlsx", sheetName = "Feuil1")
kable(jobsdf[1:10,])
```

## Job family where most people are hired

Let's see how often the same job families are wanted:

```{r, echo=FALSE}
plot <- ggplot(jobsdf, aes(x = jobsdf$Job.Family)) + geom_bar() + theme(axis.text.x  = element_text(angle=90, vjust=0, hjust = 1))
plot
```

more specific let's pull up the top 10

```{r, echo=FALSE}
tbl_jobs <- count(jobsdf$Job.Family)
most_wanted_jobs <- tbl_jobs[order(-tbl_jobs$freq),]
kable(most_wanted_jobs[1:10,])
```

## Minimum number of years of experience for recruitment and quantity of people hired per level

The dataframe also indicates the job level wanted but I had to look up what it means:

http://www.unfpa.org/resources/united-nations-staff-categories

Professional  (P) and Director (D) staff

P1 - No work experience required

P2 - Minimum of 2 years of work experience

P3 - Minimum of 5 years of work experience

P4 - Minimum of 7 years of work experience

P5 - Minimum of 10 years of work experience

D1 - Minimum of 15 years of work experience

D2 - More than 15 years of work experience

General Service  (G) staff

G1 - No work experience required

G2 - Minimum of 2 years of work experience

G3 - Minimum of 3 years of work experience

G4 - Minimum of 4 years of work experience

G5 - Minimum of 5 years of work experience

G6 - Minimum of 6 years of work experience

G7 - Minimum of 7 years of work experience

National Professional  Officers (NO)

NOA - No work experience required

NOB - Minimum of 2 years of work experience

NOC - Minimum of 5 years of work experience

NOD - Minimum of 7 years of work experience

```{r, echo=FALSE}
plot <- ggplot(jobsdf, aes(x = jobsdf$Level)) + geom_bar() + theme(axis.text.x  = element_text(angle=90, vjust=0, hjust = 1))
plot
```

So the most wanted kind of job is P3 - Minimum of 5 years of work experience followed by P4 - Minimum of 7 years of work experience. The number of P2 is very limited as is any position as director. It looks like none of us are going to be recruted right after PhD!

## Countries where most people are recruited

```{r, echo=FALSE}
plot <- ggplot(jobsdf, aes(x = jobsdf$Duty.station)) + geom_bar() + theme(axis.text.x  = element_text(angle=90, vjust=0, hjust = 1))
plot
```

A vast majority of people are recruited at the main headquarters in New York, and most of the rest in Geneva, the others are not recruiting very much.
 
## Department office where most people are recruited 
 
```{r, echo=FALSE}
tbl <- data.frame(table(jobsdf$Department.Office))
kable(tbl[tbl$Freq > 10,])
```

# internships dataframe
 
Now let's look at internships:

```{r, echo=FALSE}
internshipsdf <- read.xlsx("UNO_jobs_internships.xlsx", sheetName = "Feuil1")
kable(internshipsdf[1:10,])
```


```{r, echo=FALSE}
tbl <- data.frame(table(internshipsdf$Department.Office))
kable(tbl[tbl$Freq > 10,])
```




```{r, echo=FALSE}
plot <- ggplot(internshipsdf, aes(x = internshipsdf$Duty.station)) + geom_bar() + theme(axis.text.x  = element_text(angle=90, vjust=0, hjust = 1))
plot
```

For internships the tendency is a little bit different, the proportion in New york is less compared to Bankok and Geneva which recruit the same number of interns. Cities like Vienna also stand out more. So for internships although New York is still vastly where the majority of interns end up it is less overwhelming than for actual jobs.